Computer Science House By-Laws

### 2017-02-09 bylaws.tex

% BY-LAW II - GENERAL OPERATIONS OF THE HOUSE
\bylaw{General Operations of the House}
\bsection{Standard Operating Session}
The Standard Operating Session for Computer Science House is during the thirty weeks of Fall and Spring semesters.
The Summer Sessions, Intersessions, Institute breaks, and all end of Semester Exam Weeks are considered non-standard operating sessions.
Unless explicitly stated otherwise, the requirements and expectations defined in the constitution are for the Standard Operating Session.

% BY-LAW III - OPERATIONS OF THE FINANCIAL DIRECTORSHIP
\bylaw{Operations of the Financial Directorship}
\bsection{Amount of House Dues}
The amount of dues for Active Members will be eighty dollars (\$80.00) per Academic Semester.
\bsection{Collection of House Dues}
The collection period of house dues will be decided in conjunction with The Center for Residence Life and Housing Operations.
During the dues collection period, dues for on-floor members (for both semesters) are collected through the member’s RIT bill.
Dues for off-floor members are to be collected during this period as well by the Financial Director.
For any member who moves on or off-floor during the year, any difference between dues paid and dues owed should be collected.
Dues for any alumnus/alumnae in good standing are to be collected when intention to pay is expressed to the Financial Director.
\\*\\*
If a member is unable to pay dues upon request, they may appeal their situation to the Financial Director.
If the Financial Director deems their situation appropriate, they may grant an extension for payment.
If the Financial Director deems their situation inappropriate for extension, the member may appeal to the Executive Board.
If the Executive Board disagrees with the Financial Director, the Executive Board may grant an extension.
If the Executive Board agrees with the Financial director, the member’s payment is considered delinquent and the member’s privileges are revoked until payment can be made.
This process may be repeated indefinitely at the discretion of the Financial Director and the Executive Board.
\\*\\*
All dues must be collected in full before the annual membership evaluation (\ref{Membership Evaluation}). After this date, dues collection is suspended until the start of the next academic year.
\bsection{Breakdown of Dues for Directorship Budgets}
\begin{center}
\begin{tabular}[c]{l c}
Directorship Name & Percentage of Dues \\
\hline
\hline
Operational Communications & 20\% \\
\hline
Evaluations \& Selections & 5\% \\
\hline
House History & 10\% \\
\hline
House Improvements & 15\% \\
\hline
Research and Development & 20\% \\
\hline
Social & 20\% \\
\hline
Accumulated & 10\% \\
\hline
\end{tabular}
\end{center}

The suggested total operational budget is \$8064.
This figure is based on yearly estimated on-floor member dues (\$160 x 56 members = \$8960) minus the 10\% reserved for Accumulated (Accum).
Money allocated for Accum and off-floor member dues is deposited into the CSH Account and saved.

@@

% BY-LAW IV - OPERATIONS OF THE EVALUATIONS DIRECTORSHIP
\bylaw{Operations of the Evaluations Directorship}
\bsection{The Introductory Process}
The Introductory Process is designed to provide an easy means for introductory members to meet existing House members, learn House history, demonstrate their involvement potential to House, and allow existing House members to evaluate them for Active Membership.
\bsubsection{The Evaluation Period}
The Process lasts between six (6) and ten (10) weeks, starting when the Evaluations Director initiates it.
The Executive Board may hold a closed ballot Simple Majority vote to extend the Introductory Process.
\bsubsection{The Introductory Project}
Introductory members are expected to demonstrate initiative and an ability to work well in a group environment through the Introductory Project.
\bsubsection{Introductory Executive Board}
An Introductory Executive Board is elected by the introductory members to lead and manage the project, represent the introductory project participants to House, and evaluate participants based on their contribution to the project.
The Introductory Executive Board consists of three members:
\begin{itemize}
	\item A President, who leads the project and acts as primary representative to House through weekly status reports at House Meeting.
	\item A Vice President, who assists the President in leadership and representation.
	\item A Treasurer, who manages the finances for the project.
\end{itemize}
Introductory Members also elect a Secretary to take notes, and any number of additional non-voting leaders may be elected to take on project-specific tasks.
\bsubsubsection{The Project} 
The Project is an annual fundraising event that takes place in the first semester of the Introductory Process.
All of the proceeds go to a charity chosen in advance by the participants.
The Executive Board is encouraged to discuss the Project and following an open ballot Simple Majority Vote, may choose to intervene in the Introductory Project if the Project does not appear to fulfill requirements.
\bsubsubsection{Introductory Project Advisors} 
The Evaluations Director may choose between one (1) and three (3) House members to be Introductory Project Advisors.
The advisors assist in organizing the participants at the beginning of the Introductory Project and thereafter act as a resource to keep the Project running smoothly.
\bsubsection{The Introductory Packet}
Each Introductory Process participant, after the first week, is given two (2) weeks to return a document that should contain the following:
\begin{itemize}
	\item A signature from all Active/Introductory Resident members, each Executive Board member, and fifteen (15) of any combination of the following:
	\begin{itemize}
		\item Non-Resident members who have passed a Membership Evaluation 
		\item Alumni members (not including Non-Resident Executive Board members)
		\item Honorary members
		\item Advisory members
	\end{itemize}
	\item A description of each Executive Board position, including:
	\begin{itemize}
		\item The responsibilities of the position
		\item The name(s) of the position’s member(s)
		\item The position’s weekly meeting time
	\end{itemize}
	\item A list of seven (7) annual House social events
	\item A list of seven (7) major House technical achievements
\end{itemize}
\bsubsection{Expectations of an Introductory Member}
Before the end of the Process, an Introductory Member is expected to:
\begin{itemize}
\item Attend all House meetings during the process
\item Complete the Introductory Packet
\item Be an active participant in the Introductory Project
\item Attend at least one House directorship meeting for each week of the process
\item Attend at least one House social event during the process
\item Attend at least two seminars relating to computing or electronics
\item Sign a copy of the Membership Agreement describing a House Member’s responsibilities and expectations.
\end{itemize}

>>>>

% BY-LAW II - GENERAL OPERATIONS OF THE HOUSE
\bylaw{General Operations of the House}
\bsection{Standard Operating Session}
The Standard Operating Session for Computer Science House is during the thirty weeks of Fall and Spring semesters.
The Summer Sessions, Intersessions, Institute breaks, and all end of Semester Exam Weeks are considered non-standard operating sessions.
Unless explicitly stated otherwise, the requirements and expectations deﬁned in the constitution are for the Standard Operating Session.

% BY-LAW III - OPERATIONS OF THE FINANCIAL DIRECTORSHIP
\bylaw{Operations of the Financial Directorship}
\bsection{Amount of House Dues}
The amount of dues for Active Members will be eighty dollars (\$80.00) per Academic Semester.
\bsection{Collection of House Dues}
The collection period of house dues will be decided in conjunction with The Center for Residence Life and Housing Operations.
During the dues collection period, dues for on-floor members (for both semesters) are collected through the member’s RIT bill.
Dues for off-floor members are to be collected during this period as well by the Financial Director.
For any member who moves on or off-floor during the year, any difference between dues paid and dues owed should be collected.
Dues for any alumnus/alumnae in good standing are to be collected when intention to pay is expressed to the Financial Director.
\\*\\*
If a member is unable to pay dues upon request, they may appeal their situation to the Financial Director.
If the Financial Director deems their situation appropriate, they may grant an extension for payment.
If the Financial Director deems their situation inappropriate for extension, the member may appeal to the Executive Board.
If the Executive Board disagrees with the Financial Director, the Executive Board may grant an extension.
If the Executive Board agrees with the Financial director, the member’s payment is considered delinquent and the member’s privileges are revoked until payment can be made.
This process may be repeated indefinitely at the discretion of the Financial Director and the Executive Board.
\\*\\*
All dues must be collected in full before the annual membership evaluation (\ref{Membership Evaluation}). After this date, dues collection is suspended until the start of the next academic year.
\bsection{Derivation of Directorship Budgets}
The total operational budget is to be defined by the Financial Director based on dues collection. The budget below outlines the percentage allotment for each director. 
\begin{center}
\begin{tabular}[c]{l c}
Directorship Name & Percentage of Dues \\
\hline
\hline
Operational Communications & 20\% \\
\hline
Evaluations \& Selections & 5\% \\
\hline
House History & 10\% \\
\hline
House Improvements & 20\% \\
\hline
Research and Development & 15\% \\
\hline
Social & 20\% \\
\hline
Addition to Accumulated Funds& 10\% \\
\hline
\end{tabular}
\end{center}
During the Operating Session, the Financial Director may propose an amended distribution that must be approved by a Simple Majority Executive Board vote.

@@

% BY-LAW IV - OPERATIONS OF THE EVALUATIONS DIRECTORSHIP
\bylaw{Operations of the Evaluations Directorship}
\bsection{The Introductory Process}
The Introductory Process is designed to provide an easy means for introductory members to meet existing House members, learn House history, demonstrate their involvement potential to House, and allow existing House members to evaluate them for Active Membership.
\bsubsection{The Evaluation Period}
The Process lasts between six (6) and ten (10) weeks, starting when the Evaluations Director initiates it.
The Executive Board may hold a closed ballot Simple Majority vote to extend the Introductory Process.
\bsubsection{The Introductory Project}
Introductory members are expected to demonstrate initiative and an ability to work well in a group environment through the Introductory Project.
\bsubsection{Introductory Executive Board}
An Introductory Executive Board is elected by the introductory members to lead and manage the project, represent the introductory project participants to House, and evaluate participants based on their contribution to the project.
The Introductory Executive Board consists of three members:
\begin{itemize}
	\item A President, who leads the project and acts as primary representative to House through weekly status reports at House Meeting.
	\item A Vice President, who assists the President in leadership and representation.
	\item A Treasurer, who manages the finances for the project.
\end{itemize}
Introductory Members also elect a Secretary to take notes, and any number of additional non-voting leaders may be elected to take on project-specific tasks.
\bsubsubsection{The Project} 
The Project is an annual fundraising event that takes place in the first semester of the Introductory Process.
All of the proceeds go to a charity chosen in advance by the participants.
The Executive Board is encouraged to discuss the Project and following an open ballot Simple Majority Vote, may choose to intervene in the Introductory Project if the Project does not appear to fulfill requirements.
\bsubsubsection{Introductory Project Advisors} 
The Evaluations Director may choose between one (1) and three (3) House members to be Introductory Project Advisors.
The advisors assist in organizing the participants at the beginning of the Introductory Project and thereafter act as a resource to keep the Project running smoothly.
\bsubsection{The Introductory Packet}
Each Introductory Process participant, after the first week, is given two (2) weeks to return a document that should contain the following:
\begin{itemize}
	\item A signature from all Active/Introductory Resident members, each Executive Board member, and fifteen (15) of any combination of the following:
	\begin{itemize}
		\item Non-Resident members who have passed a Membership Evaluation 
		\item Alumni members (not including Non-Resident Executive Board members)
		\item Honorary members
		\item Advisory members
	\end{itemize}
	\item A description of each Executive Board position, including:
	\begin{itemize}
		\item The responsibilities of the position
		\item The name(s) of the position’s member(s)
		\item The position’s weekly meeting time
	\end{itemize}
	\item A list of seven (7) annual House social events
	\item A list of seven (7) major House technical achievements
\end{itemize}
\bsubsection{Expectations of an Introductory Member}
Before the end of the Process, an Introductory Member is expected to:
\begin{itemize}
\item Attend all House meetings during the process
\item Complete the Introductory Packet
\item Be an active participant in an the Introductory Project
\item Attend at least one House directorship meeting for each week of the process
\item Attend at least one House social event during the process
\item Attend at least two seminars relating to computing or electronics
\item Sign a copy of the Membership Agreement describing a House Member’s responsibilities and expectations.
\end{itemize}
